
\charm{Blossom of Inevitable Demise}
{3m}
{Supplemental}{Instant}{-}
{Righteous Devil 3, Essence 1}
This charm supplements a Righteous Devil Style attack with a Firewand.
It allows the martial artist to attack from Medium Range, though this still requires an aim action as usual.

\charm{Cloud of Ebon Devils}
{2m}
{Supplemental}{Instant}{Mastery}
{Righteous Devil 2, Essence 1}
This charm supplements an aim action with a firewand.
When she does so, she may reflexively draw her weapon, or reflexively reload it.
This charm cannot be used if an enemy is within close range.

\textbf{Mastery}: Cloud of Ebon devils can be used to supplement a join battle roll.
This allows the martial artist to reflexively aim and draw her weapon.

%\charm{Kiss of Sun Concentration}
% {3m}
% {Supplemental}{Instant}{Mastery}
% {Righteous Devil 2, Essence 1}
 
\charm{Righteous Devil Form}
{5m}
{Simple}{One Scene}{Form, Psyche}
{Righteous Devil 3, Essence 2, Blossom of inevitable Demise, Cloud of Ebon Devils}
The first time the Righteous Devil enters this form in a scene,
She may roll an instill action against all enemies in combat with her with (Essence) automatic successes.
This instill action must be used to intimidate or otherwise inspire with shame, guilt, or remorse as appropriate to their sins.
For the rest of the scene, any characters who possesses this intimacy takes a penalty equal to the stylist's Charisma on disengage, withdraw, or stealth-based actions.
Additionally, At the beginning of each turn, the righteous devil may take a reflexive aim action against any enemy who possesses this intimacy.

The Martial Artist may also use a firewand effectively in close combat.
Used in this way, treat the firewand as a medium weapon with bashing, martial arts, and shield tags.
The martial artist may also affix a bayonet to gain the lethal tag.
While this use is not compatible with effects that specifically modify ranged attacks, it can still benefit from other charms of this or other staff or spear compatible styles.

\textbf{Mastery}: Whenever the stylist successfully lands a decisive attack after taking an aim action,
she may reflexively activate Righteous Devil Form.

\charm{Azure Abacus Meditation}
{4m, 1wp}
{Supplemental}{Instant}{Terrestrtial}
{Righteous Devil 5, Essence 2, Righteous Devil Form}
This charm supplements a withering attack roll that also benefits from extra dice from an Aim action.
Its effects depend on the enemy's level of cover.

\begin{description}
\item[No Cover] The attack ignores all soak that does not come from charms or other magical effects.
Artifact Armor is explicitly not a magical effect.
\item[Light Cover] The attack ignores half of the enemy's mundane soak.
\item[Heavy Cover] The attack ignores 1 soak for every success rolled, up to half the target's full value.
\item[Full Cover] No effect.
\end{description}

\textbf{Terrestrial}: All targets are considered to be in at least light cover.

\charm{Burning Judgment Halo}
{5m, 4i}
{Simple}{Instant}{Perilous, Mastery}
{Righteous Devil 4, Essence 3, Righteous Devil Form}
This charm creates a ring of flames that encompasses all characters at close range.
The flames need not be a complete circle.
They stylist can instead choose to create an arc or semi-circle.
This ring of fire is an environmental hazard that requires a difficulty 5 (Stamina + Resistance) roll to cross.
Anyone too close to the flames or attempting to cross take 4 lethal damage (post-soak).
The Righteous Devil is immune to the flames.

The flames created by this charm last until the Righteous Devil's next turn unless she pays an additional four initiative to renew it at the start of each of her turns.

\textbf{Mastery}: The flames created by this charm will continue to burn for as long as the Righteous Devil remains at its center.
Once she moves from that point, the flames will burn for a single round more.

\charm{Dancing Devil Trigger Finger}
{10m, 3i, 1wp}
{Simple}{Instant}{Perilous, Mastery, Once/Scene}
{Righteous Devil 4,  Essence 3, Righteous Devil form}
This charm supplements a decisive attack allows the Righteous Devil to attack multiple targets.
The Martial Artist may attack  up to
1 enemy at close range,
2 enemies at short range,
and three enemies at medium range
(If extended using `Blossom of Inevitable Demise`),
so long as it makes sense to.
She makes a single \textbf{Decisive} attack roll,
rolling damage separately against each enemy.

The Martial Artist must divide her initiative evenly among all targeted enemies,
and cannot assign more than (Essence + 3) initiative to any single enemy.
Any additional initiative that cannot be assigned is turned into motes after the attack.

\textbf{Mastery}: The Martial Artist need not divide her initiative.
Each target faces the full possible damage.

\charm{Caress of 1,000 Hells}
{6m, 1wp}
{Supplemental}{Instant}{Aggravated, Mastery}
{Righteous Devil 5, Essence 3, Azure Abacus Meditation, Burning Judgment Halo, Dancing Devil Trigger Finger}
This charm supplements a Decisive attack.
If the attack is successful, the target must choose to repent or burn.

If they choose to repent, the target forms a Defining intimacy reflecting the nature of his atonement,
chosen by that character's player.
A Guild Merchant Prince who has made his fortune in the slave trade might form a defining tie of hatred for all slavers,
while a hedonistic Abyssal Mass Murderer might form a defining Principle of pacifism.
A repentant enemy will generally retreat or surrender.
If he chooses to reestablish hostilities, he crashes and his initiative is set to -10.

If the enemy chooses to burn, he suffers (Essence) aggravated damage in addition to the damage of the attack.

\textbf{Mastery}: The target suffers health levels of aggravated damage instead of dice
